AFQ-Insight

### 2019-12-16 reports/manuscript/sections/introduction.tex
Update reports/manuscript/sections/introduction.tex

To relate the diffusion in each voxel to the macro-structure of
long-range connections between different brain regions, methods for
computational tract-tracing from diffusion MRI, or tractography, combine
the estimates of fascicle orientations in each voxel to form streamlines
that traverse the volume of the white matter \cite{Conturo1999-je,
Mori2002-qi}. These methods have been under increased scrutiny and
several lines of investigation have raised critiques of their validity
\cite{Maier-Hein2017-vb, Thomas2014-ki}. On the other hand, there
have been efforts to shore up the inferences made with these methods
\cite{Pestilli2014NatMeth, Takemura2016-sh, Smith2013-nc, Smith2015-cx,
Smith2015-zt, Rheault2018-wk}. Importantly, though discovering novel
nerve fiber tracts requires extraordinary evidence, and delineating
the exact cortical termination of the streamlines in the gray matter
is still prone to error, there is little dispute that tractography
can accurately define the location of several major white matter
tracts that are known to exist within the core of the white matter
\cite{Maier-Hein2017-vb}.

>>>>

To relate the diffusion in each voxel to the macro-structure of
long-range connections between different brain regions, methods for
computational tract-tracing from diffusion MRI, or tractography, combine
the estimates of fiber orientations in each voxel to form streamlines
that traverse the volume of the white matter \cite{Conturo1999-je,
Mori2002-qi}. These methods have been under increased scrutiny and
several lines of investigation have raised critiques of their validity
\cite{Maier-Hein2017-vb, Thomas2014-ki}. On the other hand, there
have been efforts to shore up the inferences made with these methods
\cite{Pestilli2014NatMeth, Takemura2016-sh, Smith2013-nc, Smith2015-cx,
Smith2015-zt, Rheault2018-wk}. Importantly, though discovering novel
nerve fiber tracts requires extraordinary evidence, and delineating
the exact cortical termination of the streamlines in the gray matter
is still prone to error, there is little dispute that tractography
can accurately define the location of several major white matter
tracts that are known to exist within the core of the white matter
\cite{Maier-Hein2017-vb}.
